MCTS Based on Simple Regret

### 2012-02-22 slides/slides.tex
final changes to the slides

\begin{frame}{UCB vs. $\epsilon$-greedy vs UVB}
\begin{figure}[h]
\centering
\includegraphics[scale=0.45]{onelevel-64.pdf}

64 Bernoulli arms, randomly generated
\end{figure}
\end{frame}

\begin{frame}{Doing Better Than UCT on Trees}
Uniform sampling is useless in this tree:
\begin{figure}[h]
\centering
\includegraphics[scale=0.8]{twolevel-tree.pdf}
\end{figure}
Rational sampling:
\begin{itemize}
\item first, choose an action that maximizes VOI (UVB);
\item then, choose actions that maximize average reward (UCB).
\end{itemize}
\end{frame}{}

\begin{frame}{UVT vs. VCT (UVB+UCT) vs. UCT}
\begin{figure}[h]
\centering
\includegraphics[scale=0.45]{twolevel-64.pdf}

64 Bernoulli arms, randomly generated
\end{figure}
\end{frame}

>>>>

\begin{frame}{Sailing domain}
\begin{itemize}
\item A square lake.
\item A sailboat has to find the shortest path between corners.
\item The wind changes randomly.
\end{itemize}
\begin{figure}[h!]
  \begin{minipage}[b]{0.45\linewidth}
    \centering
    \includegraphics[scale=0.32]{costs-size=6-group=median.pdf}\\
    {\scriptsize Fig. 1: Median cost}
  \end{minipage}
  \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[scale=0.32]{costs-size=6-group=minimum.pdf}\\
    {\scriptsize Fig. 2: Minimum cost}
  \end{minipage}
  \label{fig:sailing-cost-vs-nsamples}
\end{figure}
\begin{itemize}
\item UCT is always worse than $\frac 1 2$-greedy+UCT or
UCB$_{\sqrt{\cdot}}$+UCT. 
\item UCT is sensitive to the value of $c$: the median cost is
much higher than the minimum cost.
\end{itemize}
\end{frame}

\begin{frame}{VOI-aware MCTS}
\begin{figure}[h]
  \centering
  \includegraphics[scale=0.6]{tree-identity-k=32-uqb=8+voi.pdf}\\
\end{figure}
\begin{itemize}
\item The experiments were performed on
randomly generated trees.
\item VOI+UCT, the scheme based on a VOI estimate,
outperforms all other sampling schemes in this example.
\end{itemize}
\end{frame}
